### 2014-01-21 disc_arfi_mr.tex
integrtaed Ned's changes

We did not expect perfect agreement between MR and ARFI imaging volume or
tri-axial dimensions since each modality applies a different amount of external
compression to the rectal wall, which then deforms the prostate.  Pressure on
the prostate during ARFI imaging is modulated by the urologist when he locks
the transducer rotation apparatus in place prior to imaging, and deformation of
the prostate can be easily visualized during this alignment process.  It was
our goal to apply as little pressure while still maintaining uniform contact
throughout the image acquisition. This is critical since poor acoustic coupling
to the prostate through the rectal wall can greatly diminish ARFI image
displacement SNR.

>>>>

We did not expect perfect agreement between MR and ARFI imaging volume or
tri-axial dimensions since each modality applies a different amount of external
compression to the rectal wall, which then deforms the prostate.  Pressure on
the prostate during ARFI imaging is modulated by the urologist when the
transducer rotation apparatus is locked into position prior to imaging, and
deformation of the prostate can be easily visualized during this alignment
process.  It was our goal to apply as little pressure while still maintaining
uniform contact throughout the image acquisition. This is critical since poor
acoustic coupling to the prostate through the rectal wall can greatly diminish
ARFI image displacement SNR.

### 2014-01-21 intro.tex
integrtaed Ned's changes

Acoustic Radiation Force Impulse (ARFI) imaging is an ultrasound-based modality
that evaluates the mechanical properties of tissues.~\cite{Nightingale2002b}
ARFI imaging has the potential to aid in PCa diagnosis and management by
evaluating the structural composition of prostate zones and tumors based on
their stiffness contrast.  Zhai \etal were able to visualize prostatic anatomy
by utilizing ARFI imaging in freshly-excised prostates. In a second study, Zhai
\etal demonstrated the feasibility of ARFI prostate imaging
\invivo~\cite{Zhai2012}; however, to the authors’ best knowledge, there have
been no studies to date that compare \invivo ARFI prostate imaging to other
imaging modalities.~\cite{Zhai2010}

>>>>

Acoustic Radiation Force Impulse (ARFI) imaging is an ultrasound-based modality
that evaluates the mechanical properties of tissues.~\cite{Nightingale2002b}
ARFI imaging has the potential to aid in PCa diagnosis and management by
evaluating the structural composition of prostate zones and tumors based on
their stiffness contrast.  Zhai \etal~were able to visualize prostatic anatomy
by utilizing ARFI imaging in freshly-excised prostates. In a second study, Zhai
\etal~demonstrated the feasibility of ARFI prostate imaging
\invivo~\cite{Zhai2012}; however, to the authors’ best knowledge, there have
been no studies to date that compare \invivo ARFI prostate imaging to other
imaging modalities.~\cite{Zhai2010}
